Who does big team science?

### 2023-11-01 manuscript_scopus.Rmd
updated formatting

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
# header-includes:
csl               : "includes/nature.csl"
# documentclass     : "apa7"
output            : papaja::apa6_pdf
appendix          :
  - "appendix.Rmd"
---

@@

***Education***. We collected degree information from the author table.
Information on this variable is in the appendix.

***Types of Publications***. We took information from the publication
type variable for each author's publications to present information
about the types of papers BTS authors publish. Information on this
variable is in the appendix.

***Publication Metrics***. For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.

***Institutions***. We report the number of institutions involved in big team science publications.

### RQ4: Author Diversity Statistics \

***Seniority***. Career length for each author was defined as the
year of the first publication minus the current year listed for each
author. Number of publications included the number of unique entries an author was included in the database. Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar to assess if only senior scholars were

***Geopolitical Region***. Geopolitical region was created by binning country code identifiers into the 17 identified United Nation Regions.

@@

*Number of articles*. The total number of articles included in this
analysis was `r total_num` including `r health_num` Health Sciences
articles, `r physical_num` Physical Sciences articles, `r social_num`
Social Sciences articles, and `r life_num` Life Sciences articles.
Articles could be classified into multiple categories. Figure
\@ref(fig:fig-pub-time) shows the number of articles published across
time for each of the four large subject areas.

@@

*Number of journals*. The number of distinct journals big team science
articles were published in was `r journals` with `r health_journal`
journals in Health Sciences, `r physical_journal` journals in Physical
Sciences, `r social_journal` journals in Social Sciences, and
`r life_journal` journals in Life Sciences. The descriptive statistics
for the Source Normalized Impact per Paper is presented in the
supplemental materials with a comparison for all papers.

@@

***Publication Metrics***. The average number of publications by authors on big team science papers
is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
publication counts were averaged across authors for each publication,
and then these average publication counts were averaged across
publications *M* = `r avg_pub_count_paper` (*SD* =
`r sd_pub_count_paper`). The average variability (i.e., the average
standard deviation with authors of a manuscript) with publication counts
of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
`r SD_SD_pub_count_paper`).

@@

***Institutions***. The total number of unique affiliation across all papers was `r affs`.

@@

***Seniority***. Figure \@ref(fig:fig-career) portrays the average career length for
authors involved in BTS publications across years. Career length was
defined as the year of first publication minus the current year, and
higher numbers mean longer careers. To analyze trends over time, we
calculated the average career length for each publication (i.e., average
author career lengths to create one score for each paper) and analyzed a
regression analysis using career length to predict year of publication.
In order to show variance between individuals, we calculated the
standard deviation of career length for each publication and used this
variance as an additional predictor.

@@

***Geopolitical Regions***.

@@

@@

Our investigation expands into an exploration of the researchers who
publish in big teams focusing on career length, publication metrics, and
geopolitical affiliation. The number of earlier career scholars is
increasing in publications across the years, indicating that big teams
may be more accessible to different types of individuals, not just
older, more established researchers. This result is especially
interesting given the publish-or-perish model still present in most
institutions, as it may seem that large-scale projects could be a risky
choice for non-permanent researchers. In the authors' experience, big
team projects are often quite slow to publication, incentives may be low
for non corresponding authors if institutions do not value papers
without lead authorship, and there is no guarantee for publication even
with a large group. However, with a large team the distribution of work
could imply less effort on individual non-leading members, and research
has shown that larger-team publications do receive more citations and
appear to have higher impact [@larivière2015].

>>>>

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
appendix          :
  - "appendix.Rmd"

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

#### Education

We collected degree information from the author table.
Information on this variable is in the appendix.

#### Types of Publications

We took information from the publication
type variable for each author's publications to present information
about the types of papers BTS authors publish. Information on this
variable is in the appendix.

#### Publication Metrics

For each author, we calculated the number of publications and the h-index. The h-index represents the highest *h* number of publications that have at least *h* citations.

#### Institutions

We report the number of institutions involved in big team science publications.

### RQ4: Author Diversity Statistics

#### Seniority

Career length for each author was defined as the
year of the first publication minus the current year listed for each
author. Number of publications included the number of unique entries an author was included in the database. Career length and number of publications was used as a proxy for the "age" or "seniority" of a scholar.

#### Geopolitical Region

Geopolitical region was created by binning country code identifiers into the 17 identified United Nation subregions.

@@

### Number of articles

The total number of articles included in this
analysis was `r total_num` including `r health_num` Health Sciences
articles, `r physical_num` Physical Sciences articles, `r social_num`
Social Sciences articles, and `r life_num` Life Sciences articles.
Articles could be classified into multiple categories. Figure
\@ref(fig:fig-pub-time) shows the number of articles published across
time for each of the four large subject areas.

@@

### Number of journals

The number of distinct journals big team science
articles were published in was `r journals` with `r health_journal`
journals in Health Sciences, `r physical_journal` journals in Physical
Sciences, `r social_journal` journals in Social Sciences, and
`r life_journal` journals in Life Sciences. The descriptive statistics
for the Source Normalized Impact per Paper is presented in the
supplemental materials with a comparison for all papers.

@@

### Publication Metrics

The average number of publications by authors on big team science papers
is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
publication counts were averaged across authors for each publication,
and then these average publication counts were averaged across
publications *M* = `r avg_pub_count_paper` (*SD* =
`r sd_pub_count_paper`). The average variability (i.e., the average
standard deviation with authors of a manuscript) with publication counts
of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
`r SD_SD_pub_count_paper`).

@@

### Institutions

The total number of unique affiliation across all papers was `r affs`.

@@

### Seniority

Figure \@ref(fig:fig-career) portrays the average career length for
authors involved in BTS publications across years. Career length was
defined as the year of first publication minus the current year, and
higher numbers mean longer careers. To analyze trends over time, we
calculated the average career length for each publication (i.e., average
author career lengths to create one score for each paper) and analyzed a
regression analysis using career length to predict year of publication.
In order to show variance between individuals, we calculated the
standard deviation of career length for each publication and used this
variance as an additional predictor.

@@

@@

### Geopolitical Regions

@@

Our investigation expands into an exploration of the researchers who
publish in big teams focusing on diversity in seniority of authors and
geopolitical affiliation. The number of earlier career scholars is
increasing in publications across the years, indicating that big teams
may be more accessible to different types of individuals, not just
older, more established researchers. This result is especially
interesting given the publish-or-perish model still present in most
institutions, as it may seem that large-scale projects could be a risky
choice for non-permanent researchers. In the authors' experience, big
team projects are often quite slow to publication, incentives may be low
for non corresponding authors if institutions do not value papers
without lead authorship, and there is no guarantee for publication even
with a large group. However, with a large team the distribution of work
could imply less effort on individual non-leading members, and research
has shown that larger-team publications do receive more citations and
appear to have higher impact [@larivière2015].
